---
title: "Seurat Integration"
author: "MG"
date: '2023-1-17'
output: html_document
---
# Seurat Integration Workflow

## 1. Load Packages
```{r setup, include=FALSE, warning=FALSE}
library(RColorBrewer)
library(sctransform)
library(ggplot2)
library(dplyr)
library(Seurat)
library(tidyseurat)
library(patchwork)
library(magrittr)
library(data.table)
library(harmony)
library(cowplot)
library(writexl)
```

## 2. Load Seurat Objects

###### These are the Vento-Tormo CD45+ decidual cells; data was downloaded and each sample was taken through the "Seurat - Guided Clustering Tutorial" then saved as an object

```{r}
vt219 <- readRDS("/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/vt219_outs/finalqc/vt219qc.rds")
vt223 <- readRDS("/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/vt223_outs/finalqc/vt223qc.rds")
```

## 3. Performing integration on datasets that were normalized with SCTransform:

-Datasets were normalized with sctransform prior to integration. readRDS was used to bring in these datasets

-Each dataset includes cells with 500 or greater detected genes

-Run the PrepSCTIntegration() function prior to identifying anchors

-When running FindIntegrationAnchors(), and IntegrateData(), set the normalization.method parameter to the value SCT.

-When running sctransform-based workflows, including integration, do not run the ScaleData() function

### Select integration features and prep step

```{r}
features <- SelectIntegrationFeatures(object.list = list(vt219, vt223), nfeatures = 3000)
vtagg <- PrepSCTIntegration(object.list = list(vt219, vt223), anchor.features = features)
```

### Find immune anchors

```{r}
immune.anchors <- FindIntegrationAnchors(object.list = vtagg, normalization.method = "SCT",
    anchor.features = features)
```

### Save the immune anchors object!

```{r}
#Save wherever you'd like
saveRDS(immune.anchors, "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/jan_219+223anchors.rds")
```

### Combine the data

```{r}
immune.combined.sct <- IntegrateData(anchorset = immune.anchors, normalization.method = "SCT")
```

### Save the combined object!

```{r}
#Save wherever you'd like
saveRDS(immune.combined.sct, "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/jan_219+223_combined_sct.rds")
```

## 4. Visualize immune.combined.sct

```{r}
immune.combined.sct[[]]
```

## 5. Perform an integrated analysis

```{r}
pcaimmune.combined.sct <- RunPCA(immune.combined.sct, verbose = FALSE)
umapimmune.combined.sct <- RunUMAP(pcaimmune.combined.sct, reduction = "pca", dims = 1:30)
```

```{r}
neighbor <- FindNeighbors(umapimmune.combined.sct, reduction = "pca", dims = 1:30)
neighbor <- FindClusters(neighbor, resolution = 0.5)
```

## 6. Save the final object!

```{r}
#Save wherever you'd like
saveRDS(neighbor, "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/jan_clustered_immune.combined.sct.rds")
```

## Loading the final clustered object from cheaha so that I can visualize it.

```{r}
neighbor <- readRDS("/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/jan_clustered_immune.combined.sct.rds")
```

## 7. UMAP
```{r}
vtfeatureintegrated_cd45pp <- DimPlot(neighbor, reduction = "umap", label = TRUE)
vtfeatureintegrated_cd45pp
```

### 7.1 Extract meta data

```{r}
## extract meta data
md <- neighbor@meta.data %>% as.data.table
knitr::kable(md, caption = "Integrated Meta Data")
write_xlsx(md, path = "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/sctfeatures_metadata.xlsx")
```
### 7.2 Determine Cell Number

```{r}
# How many cells are in each cluster
# Get cell identity classes
## count the number of cells per unique combinations of "Sample" and "seurat_clusters"
## with additional casting after the counting
totalcells <- md[, .N, by = c( "orig.ident", "seurat_clusters")] %>% dcast(., orig.ident ~ seurat_clusters, value.var = "N")
knitr::kable(totalcells, caption = "Total Cells per Cluster")
write_xlsx(totalcells, path = "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/sctfeatures_totalcells.xlsx")
```

### 7.3 Title UMAP

```{r}
finalUMAP <- vtfeatureintegrated_cd45pp + labs(title = "Clustering of Individual D6 scRNA")
```

## 8. Determine Cluster Differences

```{r}
# find markers for every cluster compared to all remaining cells, report only the positive ones
DefaultAssay(neighbor) <- 'RNA'
dcd45.markers <- FindAllMarkers(neighbor, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)

write_xlsx(dcd45.markers, path = "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6VTcleanmarker.xlsx")
```

### 8.1 Determine Specific Cluster Differences

```{r}
# find markers for every cluster compared to all remaining cells, report only the positive ones
# set minimum percent threshold at 50%
DefaultAssay(neighbor) <- 'RNA'
dcd45.markers.50pct <- FindAllMarkers(neighbor, only.pos = TRUE, min.pct = 0.50, logfc.threshold = 0.25)
write_xlsx(dcd45.markers.50pct, path = "/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6VT50pct_marker.xlsx")
```


```{r, collapse=TRUE}
#No need to rerun this as it takes a while - run once and save files
DefaultAssay(neighbor) <- 'RNA'
cellsPerClust <- as.data.frame(table(neighbor@active.ident))
colnames(cellsPerClust) <- c("Cluster", "nCells")
cellsPerClust
write.csv(cellsPerClust, file="/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/inteD6finalqc.csv")

#Overall number of cells 
sum(cellsPerClust$nCells)

```

```{r, eval=FALSE}
(clusters <- c(0, seq(1:12)))

for(i in clusters){
  cluster.markers <- FindMarkers(neighbor, ident.1 = i, min.pct = 0, logfc.threshold = 0, only.pos = F)
  write.csv(cluster.markers, file=paste0("/Volumes/Porrett2/Morgan_G/Data_Analysis/scAnalysis/JAN_VTintegration/QC_Workflow/D6_integrated_data/", i, "_Markers_RNA.csv"))
}
```

# Overview of VT scRNA-seq reanalysis from Participant D6 

**QC summary:** - Counts were processed using the standard Seurat (v4.2.0) workflow

    - Number of cells after filtering: 6326

    - RNA assay Normalized using: SCTransform

    - Filtering thresholds: nFeature_RNA > 200 & nFeature_RNA < 4000 & percent.mt < 10

    - Dims: 1:30
    
    
